Housing Market Institutions Drive Race and Ethnicity Differences in Energy Consumption

### 2015-04-03 ConferencePaper/DraftEdwardsWoods.tex
Tables now fit on page.  Graphics are now more uniform.  Bibliography is back.

% latex table generated in R 3.0.1 by xtable 1.7-4 package
% Fri Apr  3 21:06:40 2015
\begin{table}[ht]
\centering
\begin{tabular}{rrrrrr}
  \hline
 & Mobile & SFDetached & SFAttached & SmApartment & LgApartment \\ 
  \hline
FALSEWt & 371 & 5694 & 544 & 430 & 951 \\ 
  FALSEAfAm &  24 & 754 & 121 & 174 & 382 \\ 
  FALSEAsian &   1 & 231 &  48 &  52 & 113 \\ 
  FALSEMulti &   6 &  87 &  14 &  12 &  27 \\ 
  FALSENativeAm &   7 &  35 &   9 &   7 &  15 \\ 
  FALSEOther &   2 &  59 &   8 &  13 &  29 \\ 
  FALSEPacific &   1 &  22 &   1 &   2 &  10 \\ 
  TRUEAfAm &   3 &   8 &  10 &   5 &   8 \\ 
  TRUEAsian &   0 &   5 &   0 &   0 &   1 \\ 
  TRUEMulti &   1 &  10 &   2 &   4 &   4 \\ 
  TRUENativeAm &   2 &  17 &   3 &   6 &   9 \\ 
  TRUEOther &   6 &  41 &  12 &  16 &  24 \\ 
  TRUEPacific &   0 &   2 &   1 &   1 &   0 \\ 
  TRUEWt &  97 & 730 & 105 & 184 & 332 \\ 
   \hline
\end{tabular}
\caption{Count of Observations by Race and Structure Type} 
\label{tab:RaceVStruct}
\end{table}

@@

% latex table generated in R 3.0.1 by xtable 1.7-4 package
% Fri Apr  3 21:06:40 2015
\begin{table}[ht]
\centering
\begin{tabular}{rrrrr}
  \hline
 & NE & MidWest & South & West \\ 
  \hline
Mobile &  47 &  92 & 245 & 137 \\ 
  SFDetached & 1173 & 2080 & 2685 & 1757 \\ 
  SFAttached & 218 & 162 & 257 & 241 \\ 
  SmApartment & 326 & 145 & 226 & 209 \\ 
  LgApartment & 470 & 323 & 603 & 509 \\ 
   \hline
\end{tabular}
\caption{Count of Observations by Region and Structure Type} 
\label{tab:RegionVStruct}
\end{table}

@@

% latex table generated in R 3.0.1 by xtable 1.7-4 package
% Fri Apr  3 21:07:34 2015
\begin{table}[ht]
\centering
\begin{tabular}{llr}
  \hline
State & Population & Reports (per 100,000) \\ 
  \hline
Alabama & 4,677,464 & 7.50 \\ 
  Alaska & 688,125 & 13.01 \\ 
  Arizona & 6,499,377 & 3.68 \\ 
  Arkansas & 2,867,764 & 9.26 \\ 
  California & 36,580,371 & 3.03 \\ 
  Colorado & 4,935,213 & 1.97 \\ 
  Connecticut & 3,502,932 & 20.50 \\ 
  Delaware & 876,211 & 14.00 \\ 
  District of Columbia & 590,074 & 14.00 \\ 
  Florida & 18,423,878 & 3.93 \\ 
  Georgia & 9,697,838 & 2.06 \\ 
  Hawaii & 1,287,481 & 13.01 \\ 
  Idaho & 1,527,506 & 9.94 \\ 
  Illinois & 12,842,954 & 2.88 \\ 
  Indiana & 6,388,309 & 9.14 \\ 
  Iowa & 2,993,987 & 19.92 \\ 
  Kansas & 2,797,375 & 10.31 \\ 
  Kentucky & 4,287,931 & 7.50 \\ 
  Louisiana & 4,451,513 & 9.26 \\ 
  Maine & 1,319,691 & 20.50 \\ 
  Maryland & 5,658,655 & 14.00 \\ 
  Massachusetts & 6,543,595 & 4.51 \\ 
  Michigan & 10,002,486 & 4.97 \\ 
  Minnesota & 5,230,567 & 19.92 \\ 
  Mississippi & 2,940,212 & 7.50 \\ 
  Missouri & 5,956,335 & 4.99 \\ 
  Montana & 968,035 & 9.94 \\ 
  Nebraska & 1,781,949 & 10.31 \\ 
  Nevada & 2,615,772 & 5.08 \\ 
  New Hampshire & 1,321,872 & 20.50 \\ 
  New Jersey & 8,663,398 & 2.34 \\ 
  New Mexico & 1,986,763 & 5.08 \\ 
  New York & 19,467,789 & 4.60 \\ 
  North Carolina & 9,247,134 & 4.22 \\ 
  North Dakota & 641,421 & 19.92 \\ 
  Ohio & 11,528,072 & 9.14 \\ 
  Oklahoma & 3,644,025 & 9.26 \\ 
  Oregon & 3,782,991 & 13.01 \\ 
  Pennsylvania & 12,566,368 & 1.87 \\ 
  Rhode Island & 1,053,502 & 20.50 \\ 
  South Carolina & 4,503,280 & 4.22 \\ 
  South Dakota & 804,532 & 19.92 \\ 
  Tennessee & 6,240,456 & 2.61 \\ 
  Texas & 24,304,290 & 4.18 \\ 
  Utah & 2,727,343 & 9.94 \\ 
  Vermont & 621,049 & 20.50 \\ 
  Virginia & 7,795,424 & 2.03 \\ 
  Washington & 6,566,073 & 13.01 \\ 
  West Virginia & 1,814,873 & 14.00 \\ 
  Wisconsin & 5,627,610 & 1.81 \\ 
  Wyoming & 532,981 & 9.94 \\ 
   \hline
\end{tabular}
\caption{HUD Complaints per 100,000 Population} 
\label{tab:HUDComplaints}
\end{table}
\section{Conditional Demand Estimation}

@@

% latex table generated in R 3.0.1 by xtable 1.7-4 package
% Fri Apr  3 21:07:35 2015
\begin{longtable}{rrrrr}
  \hline
 & Estimate & Std. Error & t value & Pr($>$$|$t$|$) \\ 
  \hline
Income & 0.0086 & 0.0016 & 5.3662 & 0.0000 \\ 
  Income:EthRaceFALSEAfAm & 0.0031 & 0.0027 & 1.1389 & 0.2548 \\ 
  Income:EthRaceFALSEAsian & -0.0243 & 0.0034 & -7.1646 & 0.0000 \\ 
  Income:EthRaceFALSEMulti & -0.0168 & 0.0069 & -2.4259 & 0.0153 \\ 
  Income:EthRaceFALSENativeAm & 0.0117 & 0.0123 & 0.9493 & 0.3425 \\ 
  Income:EthRaceFALSEOther & -0.0249 & 0.0083 & -2.9909 & 0.0028 \\ 
  Income:EthRaceFALSEPacific & -0.0163 & 0.0138 & -1.1807 & 0.2378 \\ 
  Income:EthRaceTRUEAfAm & -0.0120 & 0.0165 & -0.7271 & 0.4672 \\ 
  Income:EthRaceTRUEAsian & -0.0365 & 0.0454 & -0.8032 & 0.4219 \\ 
  Income:EthRaceTRUEMulti & -0.0291 & 0.0212 & -1.3745 & 0.1693 \\ 
  Income:EthRaceTRUENativeAm & -0.0187 & 0.0148 & -1.2599 & 0.2077 \\ 
  Income:EthRaceTRUEOther & -0.0262 & 0.0099 & -2.6335 & 0.0085 \\ 
  Income:EthRaceTRUEPacific & -0.0122 & 0.0380 & -0.3221 & 0.7474 \\ 
  Income:EthRaceTRUEWt & -0.0192 & 0.0031 & -6.2907 & 0.0000 \\ 
  StrTenureOwnSFDetached:TOTSQFT\_EN:HDD65 & 0.0001 & 0.0000 & 4.1043 & 0.0000 \\ 
  StrTenureOwnLgApartment:TOTSQFT\_EN:HDD65 & -0.0001 & 0.0001 & -0.9580 & 0.3381 \\ 
  StrTenureOwnMobile:TOTSQFT\_EN:HDD65 & 0.0004 & 0.0001 & 5.9838 & 0.0000 \\ 
  StrTenureOwnSFAttached:TOTSQFT\_EN:HDD65 & -0.0000 & 0.0000 & -0.5516 & 0.5812 \\ 
  StrTenureOwnSmApartment:TOTSQFT\_EN:HDD65 & 0.0000 & 0.0001 & 0.5438 & 0.5866 \\ 
  StrTenureRentLgApartment:TOTSQFT\_EN:HDD65 & -0.0002 & 0.0001 & -4.0031 & 0.0001 \\ 
  StrTenureRentMobile:TOTSQFT\_EN:HDD65 & 0.0004 & 0.0002 & 1.7633 & 0.0779 \\ 
  StrTenureRentSFAttached:TOTSQFT\_EN:HDD65 & 0.0000 & 0.0001 & 0.6010 & 0.5479 \\ 
  StrTenureRentSFDetached:TOTSQFT\_EN:HDD65 & 0.0000 & 0.0000 & 0.5515 & 0.5813 \\ 
  StrTenureRentSmApartment:TOTSQFT\_EN:HDD65 & -0.0001 & 0.0001 & -1.8580 & 0.0632 \\ 
  StrTenureOwnSFDetached:TOTSQFT\_EN:CDD65 & 0.0008 & 0.0000 & 19.2068 & 0.0000 \\ 
  StrTenureOwnLgApartment:TOTSQFT\_EN:CDD65 & -0.0002 & 0.0002 & -0.8168 & 0.4140 \\ 
  StrTenureOwnMobile:TOTSQFT\_EN:CDD65 & 0.0009 & 0.0001 & 7.3167 & 0.0000 \\ 
  StrTenureOwnSFAttached:TOTSQFT\_EN:CDD65 & 0.0006 & 0.0001 & 5.0127 & 0.0000 \\ 
  StrTenureOwnSmApartment:TOTSQFT\_EN:CDD65 & 0.0001 & 0.0003 & 0.4022 & 0.6875 \\ 
  StrTenureRentLgApartment:TOTSQFT\_EN:CDD65 & 0.0000 & 0.0001 & 0.3926 & 0.6946 \\ 
  StrTenureRentMobile:TOTSQFT\_EN:CDD65 & 0.0024 & 0.0004 & 6.3205 & 0.0000 \\ 
  StrTenureRentSFAttached:TOTSQFT\_EN:CDD65 & 0.0007 & 0.0002 & 4.0210 & 0.0001 \\ 
  StrTenureRentSFDetached:TOTSQFT\_EN:CDD65 & 0.0008 & 0.0001 & 9.2680 & 0.0000 \\ 
  StrTenureRentSmApartment:TOTSQFT\_EN:CDD65 & 0.0005 & 0.0002 & 2.8365 & 0.0046 \\ 
   \hline
\hline
\caption{Orthodox kWh Model} 
\label{tab:OrthoKWHLimited}
\end{longtable}
The top parameter, Income, shows the estimate for annual kWh per dollar of income for a household headed by a non-Hispanic Caucasian.  The remaining income related variables show the deviations from this case for Hispanic headed households, labeled TRUE in the table, and by the other self reported races.  Note that in all cases, with the exception of non-Hispanic Native Americans, the parameter estimates show less electricity used than non-Hispanic Caucasian households.  Only a few of these differences are statistically significant, non-Hispanic Asian and multi-ethnic households, as well as Hispanic Caucasian households and households that reported some other race.

@@

% latex table generated in R 3.0.1 by xtable 1.7-4 package
% Fri Apr  3 21:07:36 2015
\begin{longtable}{rrrrl}
  \hline
 & Estimate & Std. Error & t value & Sig \\ 
  \hline
Income:EthRaceFALSEAfAm & 0.0052 & 0.0029 & 1.7791 &   \\ 
  Income:EthRaceFALSEAsian & -0.0230 & 0.0035 & -6.4831 & *** \\ 
  Income:EthRaceFALSEMulti & -0.0157 & 0.0057 & -2.7584 & * \\ 
  Income:EthRaceFALSENativeAm & 0.0092 & 0.0211 & 0.4382 &   \\ 
  Income:EthRaceFALSEOther & -0.0237 & 0.0082 & -2.9038 & * \\ 
  Income:EthRaceFALSEPacific & -0.0129 & 0.0230 & -0.5625 &   \\ 
  Income:EthRaceTRUEAfAm & -0.0173 & 0.0139 & -1.2454 &   \\ 
  Income:EthRaceTRUEAsian & -0.0375 & 0.0101 & -3.7155 & ** \\ 
  Income:EthRaceTRUEMulti & -0.0331 & 0.0192 & -1.7208 &   \\ 
  Income:EthRaceTRUENativeAm & -0.0163 & 0.0107 & -1.5276 &   \\ 
  Income:EthRaceTRUEOther & -0.0274 & 0.0080 & -3.4318 & ** \\ 
  Income:EthRaceTRUEPacific & -0.0240 & 0.0659 & -0.3647 &   \\ 
  Income:EthRaceTRUEWt & -0.0185 & 0.0033 & -5.5782 & *** \\ 
   \hline
\hline
\caption{System Estimation of kWh Model: Race and Ethnicity} 
\label{tab:SystemKWHEthnicity}
\end{longtable}
Table 
% \ref{tab:SystemKWHEthnicity}
shows similarites with the results from the orthodox electrity model.  Non-Hispanic Asians, and Hispanic Caucasians and Hispanic heads of households that identify as some other race all show lower electricity use per dollar of income.   This is consistent in sign with the parameter estimates in table 
% \ref{tab:ParOrthKWH}
, but the statistically significant deviations from non-Hispanic caucasions for non Hispanic multi-ethnic heads of household has vanished.  The scale of the significant paremeter estimates are also roughly the same magnitude but attenuated towards zero.

% latex table generated in R 3.0.1 by xtable 1.7-4 package
% Fri Apr  3 21:07:36 2015
\begin{longtable}{rrrrl}
  \hline
 & Estimate & Std. Error & t value & Sig \\ 
  \hline
PSQFT:OwnSFDetached:HDD65 & 0.0001 & 0.0000 & 4.4109 & *** \\ 
  PSQFT:HDD65:OwnLgApartment & 0.0000 & 0.0001 & 0.8450 &   \\ 
  PSQFT:HDD65:OwnMobile & 0.0004 & 0.0001 & 4.6205 & *** \\ 
  PSQFT:HDD65:OwnSFAttached & 0.0000 & 0.0000 & 1.3603 &   \\ 
  PSQFT:HDD65:OwnSmApartment & 0.0001 & 0.0000 & 1.1709 &   \\ 
  PSQFT:HDD65:RentLgApartment & -0.0001 & 0.0000 & -1.3292 &   \\ 
  PSQFT:HDD65:RentMobile & 0.0005 & 0.0003 & 2.0238 &   \\ 
  PSQFT:HDD65:RentSFAttached & 0.0001 & 0.0001 & 1.0923 &   \\ 
  PSQFT:HDD65:RentSFDetached & 0.0001 & 0.0000 & 1.7233 &   \\ 
  PSQFT:HDD65:RentSmApartment & -0.0000 & 0.0000 & -0.2465 &   \\ 
  PSQFT:OwnSFDetached:CDD65 & 0.0007 & 0.0000 & 16.3870 & *** \\ 
  PSQFT:OwnLgApartment:CDD65 & 0.0000 & 0.0002 & 0.2207 &   \\ 
  PSQFT:OwnMobile:CDD65 & 0.0011 & 0.0002 & 6.7660 & *** \\ 
  PSQFT:OwnSFAttached:CDD65 & 0.0005 & 0.0001 & 5.3085 & *** \\ 
  PSQFT:OwnSmApartment:CDD65 & 0.0003 & 0.0002 & 1.8671 &   \\ 
  PSQFT:RentLgApartment:CDD65 & 0.0003 & 0.0001 & 2.5551 & . \\ 
  PSQFT:RentMobile:CDD65 & 0.0020 & 0.0009 & 2.2066 &   \\ 
  PSQFT:RentSFAttached:CDD65 & 0.0009 & 0.0002 & 4.9470 & *** \\ 
  PSQFT:RentSFDetached:CDD65 & 0.0008 & 0.0001 & 8.8123 & *** \\ 
  PSQFT:RentSmApartment:CDD65 & 0.0005 & 0.0001 & 3.5753 & ** \\ 
   \hline
\hline
\caption{System Estimation of kWh Model: Square Footage} 
\label{tab:SystemKWHSQFT}
\end{longtable}
Table 
% \ref{tab:SystemKWHSQFT}
shows the relationship between heating and cooling degree days per square foot on electricity use for each of the tenure and structure type combinations.  These results are particularly troublesome because heating and cooling degree days, in conjunction with square footage, are one of the most reliable explanatory variables for electricity use.  Space heating and cooling are two major end-uses in most households.  The parameter estimates show that these reliable explanatory variables are only significant in a few rare cases.  There is a strong relationship heating and cooling degree days for owned single family detached structures, but only rented mobile homes show statistically significant reations to heating loads and only large appartments, owned or rented, for cooling loads.

@@

% Fri Apr  3 21:07:36 2015

@@

@@

\caption{Orthodox kWh Model} 

@@

% Fri Apr  3 21:07:36 2015

>>>>

% latex table generated in R 3.0.1 by xtable 1.7-4 package
% Fri Apr  3 22:03:21 2015
\begin{table}[ht]
\centering
\caption{Count of Observations by Race and Structure Type} 
\label{tab:RaceVStruct}
{\small
\begin{tabular}{rrrrrr}
  \hline
 & Mobile & SFDetached & SFAttached & SmApartment & LgApartment \\ 
  \hline
FALSEWt & 371 & 5694 & 544 & 430 & 951 \\ 
  FALSEAfAm &  24 & 754 & 121 & 174 & 382 \\ 
  FALSEAsian &   1 & 231 &  48 &  52 & 113 \\ 
  FALSEMulti &   6 &  87 &  14 &  12 &  27 \\ 
  FALSENativeAm &   7 &  35 &   9 &   7 &  15 \\ 
  FALSEOther &   2 &  59 &   8 &  13 &  29 \\ 
  FALSEPacific &   1 &  22 &   1 &   2 &  10 \\ 
  TRUEAfAm &   3 &   8 &  10 &   5 &   8 \\ 
  TRUEAsian &   0 &   5 &   0 &   0 &   1 \\ 
  TRUEMulti &   1 &  10 &   2 &   4 &   4 \\ 
  TRUENativeAm &   2 &  17 &   3 &   6 &   9 \\ 
  TRUEOther &   6 &  41 &  12 &  16 &  24 \\ 
  TRUEPacific &   0 &   2 &   1 &   1 &   0 \\ 
  TRUEWt &  97 & 730 & 105 & 184 & 332 \\ 
   \hline
\end{tabular}
}
\end{table}

@@

% latex table generated in R 3.0.1 by xtable 1.7-4 package
% Fri Apr  3 22:03:21 2015
\begin{table}[ht]
\centering
\caption{Count of Observations by Region and Structure Type} 
\label{tab:RegionVStruct}
{\small
\begin{tabular}{rrrrr}
  \hline
 & NE & MidWest & South & West \\ 
  \hline
Mobile &  47 &  92 & 245 & 137 \\ 
  SFDetached & 1173 & 2080 & 2685 & 1757 \\ 
  SFAttached & 218 & 162 & 257 & 241 \\ 
  SmApartment & 326 & 145 & 226 & 209 \\ 
  LgApartment & 470 & 323 & 603 & 509 \\ 
   \hline
\end{tabular}
}
\end{table}

@@

% latex table generated in R 3.0.1 by xtable 1.7-4 package
% Fri Apr  3 22:04:14 2015
\begin{table}[ht]
\centering
\caption{HUD Complaints per 100,000 Population} 
\label{tab:HUDComplaints}
{\small
\begin{tabular}{llr}
  \hline
State & Population & Reports (per 100,000) \\ 
  \hline
Alabama & 4,677,464 & 7.50 \\ 
  Alaska & 688,125 & 13.01 \\ 
  Arizona & 6,499,377 & 3.68 \\ 
  Arkansas & 2,867,764 & 9.26 \\ 
  California & 36,580,371 & 3.03 \\ 
  Colorado & 4,935,213 & 1.97 \\ 
  Connecticut & 3,502,932 & 20.50 \\ 
  Delaware & 876,211 & 14.00 \\ 
  District of Columbia & 590,074 & 14.00 \\ 
  Florida & 18,423,878 & 3.93 \\ 
  Georgia & 9,697,838 & 2.06 \\ 
  Hawaii & 1,287,481 & 13.01 \\ 
  Idaho & 1,527,506 & 9.94 \\ 
  Illinois & 12,842,954 & 2.88 \\ 
  Indiana & 6,388,309 & 9.14 \\ 
  Iowa & 2,993,987 & 19.92 \\ 
  Kansas & 2,797,375 & 10.31 \\ 
  Kentucky & 4,287,931 & 7.50 \\ 
  Louisiana & 4,451,513 & 9.26 \\ 
  Maine & 1,319,691 & 20.50 \\ 
  Maryland & 5,658,655 & 14.00 \\ 
  Massachusetts & 6,543,595 & 4.51 \\ 
  Michigan & 10,002,486 & 4.97 \\ 
  Minnesota & 5,230,567 & 19.92 \\ 
  Mississippi & 2,940,212 & 7.50 \\ 
  Missouri & 5,956,335 & 4.99 \\ 
  Montana & 968,035 & 9.94 \\ 
  Nebraska & 1,781,949 & 10.31 \\ 
  Nevada & 2,615,772 & 5.08 \\ 
  New Hampshire & 1,321,872 & 20.50 \\ 
  New Jersey & 8,663,398 & 2.34 \\ 
  New Mexico & 1,986,763 & 5.08 \\ 
  New York & 19,467,789 & 4.60 \\ 
  North Carolina & 9,247,134 & 4.22 \\ 
  North Dakota & 641,421 & 19.92 \\ 
  Ohio & 11,528,072 & 9.14 \\ 
  Oklahoma & 3,644,025 & 9.26 \\ 
  Oregon & 3,782,991 & 13.01 \\ 
  Pennsylvania & 12,566,368 & 1.87 \\ 
  Rhode Island & 1,053,502 & 20.50 \\ 
  South Carolina & 4,503,280 & 4.22 \\ 
  South Dakota & 804,532 & 19.92 \\ 
  Tennessee & 6,240,456 & 2.61 \\ 
  Texas & 24,304,290 & 4.18 \\ 
  Utah & 2,727,343 & 9.94 \\ 
  Vermont & 621,049 & 20.50 \\ 
  Virginia & 7,795,424 & 2.03 \\ 
  Washington & 6,566,073 & 13.01 \\ 
  West Virginia & 1,814,873 & 14.00 \\ 
  Wisconsin & 5,627,610 & 1.81 \\ 
  Wyoming & 532,981 & 9.94 \\ 
   \hline
\end{tabular}
}
\end{table}
\section{Conditional Demand Estimation}

@@

% latex table generated in R 3.0.1 by xtable 1.7-4 package
% Fri Apr  3 22:04:14 2015
{\small
\begin{longtable}{rrrrr}
\caption{Orthodox kWh Model} \\ 
  \hline
 & Estimate & Std. Error & t value & Pr($>$$|$t$|$) \\ 
  \hline
Income & 0.0086 & 0.0016 & 5.3662 & 0.0000 \\ 
  Income:EthRaceFALSEAfAm & 0.0031 & 0.0027 & 1.1389 & 0.2548 \\ 
  Income:EthRaceFALSEAsian & -0.0243 & 0.0034 & -7.1646 & 0.0000 \\ 
  Income:EthRaceFALSEMulti & -0.0168 & 0.0069 & -2.4259 & 0.0153 \\ 
  Income:EthRaceFALSENativeAm & 0.0117 & 0.0123 & 0.9493 & 0.3425 \\ 
  Income:EthRaceFALSEOther & -0.0249 & 0.0083 & -2.9909 & 0.0028 \\ 
  Income:EthRaceFALSEPacific & -0.0163 & 0.0138 & -1.1807 & 0.2378 \\ 
  Income:EthRaceTRUEAfAm & -0.0120 & 0.0165 & -0.7271 & 0.4672 \\ 
  Income:EthRaceTRUEAsian & -0.0365 & 0.0454 & -0.8032 & 0.4219 \\ 
  Income:EthRaceTRUEMulti & -0.0291 & 0.0212 & -1.3745 & 0.1693 \\ 
  Income:EthRaceTRUENativeAm & -0.0187 & 0.0148 & -1.2599 & 0.2077 \\ 
  Income:EthRaceTRUEOther & -0.0262 & 0.0099 & -2.6335 & 0.0085 \\ 
  Income:EthRaceTRUEPacific & -0.0122 & 0.0380 & -0.3221 & 0.7474 \\ 
  Income:EthRaceTRUEWt & -0.0192 & 0.0031 & -6.2907 & 0.0000 \\ 
  StrTenureOwnSFDetached:TOTSQFT\_EN:HDD65 & 0.0001 & 0.0000 & 4.1043 & 0.0000 \\ 
  StrTenureOwnLgApartment:TOTSQFT\_EN:HDD65 & -0.0001 & 0.0001 & -0.9580 & 0.3381 \\ 
  StrTenureOwnMobile:TOTSQFT\_EN:HDD65 & 0.0004 & 0.0001 & 5.9838 & 0.0000 \\ 
  StrTenureOwnSFAttached:TOTSQFT\_EN:HDD65 & -0.0000 & 0.0000 & -0.5516 & 0.5812 \\ 
  StrTenureOwnSmApartment:TOTSQFT\_EN:HDD65 & 0.0000 & 0.0001 & 0.5438 & 0.5866 \\ 
  StrTenureRentLgApartment:TOTSQFT\_EN:HDD65 & -0.0002 & 0.0001 & -4.0031 & 0.0001 \\ 
  StrTenureRentMobile:TOTSQFT\_EN:HDD65 & 0.0004 & 0.0002 & 1.7633 & 0.0779 \\ 
  StrTenureRentSFAttached:TOTSQFT\_EN:HDD65 & 0.0000 & 0.0001 & 0.6010 & 0.5479 \\ 
  StrTenureRentSFDetached:TOTSQFT\_EN:HDD65 & 0.0000 & 0.0000 & 0.5515 & 0.5813 \\ 
  StrTenureRentSmApartment:TOTSQFT\_EN:HDD65 & -0.0001 & 0.0001 & -1.8580 & 0.0632 \\ 
  StrTenureOwnSFDetached:TOTSQFT\_EN:CDD65 & 0.0008 & 0.0000 & 19.2068 & 0.0000 \\ 
  StrTenureOwnLgApartment:TOTSQFT\_EN:CDD65 & -0.0002 & 0.0002 & -0.8168 & 0.4140 \\ 
  StrTenureOwnMobile:TOTSQFT\_EN:CDD65 & 0.0009 & 0.0001 & 7.3167 & 0.0000 \\ 
  StrTenureOwnSFAttached:TOTSQFT\_EN:CDD65 & 0.0006 & 0.0001 & 5.0127 & 0.0000 \\ 
  StrTenureOwnSmApartment:TOTSQFT\_EN:CDD65 & 0.0001 & 0.0003 & 0.4022 & 0.6875 \\ 
  StrTenureRentLgApartment:TOTSQFT\_EN:CDD65 & 0.0000 & 0.0001 & 0.3926 & 0.6946 \\ 
  StrTenureRentMobile:TOTSQFT\_EN:CDD65 & 0.0024 & 0.0004 & 6.3205 & 0.0000 \\ 
  StrTenureRentSFAttached:TOTSQFT\_EN:CDD65 & 0.0007 & 0.0002 & 4.0210 & 0.0001 \\ 
  StrTenureRentSFDetached:TOTSQFT\_EN:CDD65 & 0.0008 & 0.0001 & 9.2680 & 0.0000 \\ 
  StrTenureRentSmApartment:TOTSQFT\_EN:CDD65 & 0.0005 & 0.0002 & 2.8365 & 0.0046 \\ 
   \hline
\hline
\label{tab:OrthoKWHLimited}
\end{longtable}
}
The top parameter, Income, shows the estimate for annual kWh per dollar of income for a household headed by a non-Hispanic Caucasian.  The remaining income related variables show the deviations from this case for Hispanic headed households, labeled TRUE in the table, and by the other self reported races.  Note that in all cases, with the exception of non-Hispanic Native Americans, the parameter estimates show less electricity used than non-Hispanic Caucasian households.  Only a few of these differences are statistically significant, non-Hispanic Asian and multi-ethnic households, as well as Hispanic Caucasian households and households that reported some other race.

@@

% latex table generated in R 3.0.1 by xtable 1.7-4 package
% Fri Apr  3 22:04:16 2015
{\small
\begin{longtable}{rrrrl}
\caption{System Estimation of kWh Model: Race and Ethnicity} \\ 
  \hline
 & Estimate & Std. Error & t value & Sig \\ 
  \hline
Income:EthRaceFALSEAfAm & 0.0052 & 0.0029 & 1.7791 &   \\ 
  Income:EthRaceFALSEAsian & -0.0230 & 0.0035 & -6.4831 & *** \\ 
  Income:EthRaceFALSEMulti & -0.0157 & 0.0057 & -2.7584 & * \\ 
  Income:EthRaceFALSENativeAm & 0.0092 & 0.0211 & 0.4382 &   \\ 
  Income:EthRaceFALSEOther & -0.0237 & 0.0082 & -2.9038 & * \\ 
  Income:EthRaceFALSEPacific & -0.0129 & 0.0230 & -0.5625 &   \\ 
  Income:EthRaceTRUEAfAm & -0.0173 & 0.0139 & -1.2454 &   \\ 
  Income:EthRaceTRUEAsian & -0.0375 & 0.0101 & -3.7155 & ** \\ 
  Income:EthRaceTRUEMulti & -0.0331 & 0.0192 & -1.7208 &   \\ 
  Income:EthRaceTRUENativeAm & -0.0163 & 0.0107 & -1.5276 &   \\ 
  Income:EthRaceTRUEOther & -0.0274 & 0.0080 & -3.4318 & ** \\ 
  Income:EthRaceTRUEPacific & -0.0240 & 0.0659 & -0.3647 &   \\ 
  Income:EthRaceTRUEWt & -0.0185 & 0.0033 & -5.5782 & *** \\ 
   \hline
\hline
\label{tab:SystemKWHEthnicity}
\end{longtable}
}
Table 
% \ref{tab:SystemKWHEthnicity}
shows similarites with the results from the orthodox electrity model.  Non-Hispanic Asians, and Hispanic Caucasians and Hispanic heads of households that identify as some other race all show lower electricity use per dollar of income.   This is consistent in sign with the parameter estimates in table 
% \ref{tab:ParOrthKWH}
, but the statistically significant deviations from non-Hispanic caucasions for non Hispanic multi-ethnic heads of household has vanished.  The scale of the significant paremeter estimates are also roughly the same magnitude but attenuated towards zero.

% latex table generated in R 3.0.1 by xtable 1.7-4 package
% Fri Apr  3 22:04:16 2015
{\small
\begin{longtable}{rrrrl}
\caption{System Estimation of kWh Model: Square Footage} \\ 
  \hline
 & Estimate & Std. Error & t value & Sig \\ 
  \hline
PSQFT:OwnSFDetached:HDD65 & 0.0001 & 0.0000 & 4.4109 & *** \\ 
  PSQFT:HDD65:OwnLgApartment & 0.0000 & 0.0001 & 0.8450 &   \\ 
  PSQFT:HDD65:OwnMobile & 0.0004 & 0.0001 & 4.6205 & *** \\ 
  PSQFT:HDD65:OwnSFAttached & 0.0000 & 0.0000 & 1.3603 &   \\ 
  PSQFT:HDD65:OwnSmApartment & 0.0001 & 0.0000 & 1.1709 &   \\ 
  PSQFT:HDD65:RentLgApartment & -0.0001 & 0.0000 & -1.3292 &   \\ 
  PSQFT:HDD65:RentMobile & 0.0005 & 0.0003 & 2.0238 &   \\ 
  PSQFT:HDD65:RentSFAttached & 0.0001 & 0.0001 & 1.0923 &   \\ 
  PSQFT:HDD65:RentSFDetached & 0.0001 & 0.0000 & 1.7233 &   \\ 
  PSQFT:HDD65:RentSmApartment & -0.0000 & 0.0000 & -0.2465 &   \\ 
  PSQFT:OwnSFDetached:CDD65 & 0.0007 & 0.0000 & 16.3870 & *** \\ 
  PSQFT:OwnLgApartment:CDD65 & 0.0000 & 0.0002 & 0.2207 &   \\ 
  PSQFT:OwnMobile:CDD65 & 0.0011 & 0.0002 & 6.7660 & *** \\ 
  PSQFT:OwnSFAttached:CDD65 & 0.0005 & 0.0001 & 5.3085 & *** \\ 
  PSQFT:OwnSmApartment:CDD65 & 0.0003 & 0.0002 & 1.8671 &   \\ 
  PSQFT:RentLgApartment:CDD65 & 0.0003 & 0.0001 & 2.5551 & . \\ 
  PSQFT:RentMobile:CDD65 & 0.0020 & 0.0009 & 2.2066 &   \\ 
  PSQFT:RentSFAttached:CDD65 & 0.0009 & 0.0002 & 4.9470 & *** \\ 
  PSQFT:RentSFDetached:CDD65 & 0.0008 & 0.0001 & 8.8123 & *** \\ 
  PSQFT:RentSmApartment:CDD65 & 0.0005 & 0.0001 & 3.5753 & ** \\ 
   \hline
\hline
\label{tab:SystemKWHSQFT}
\end{longtable}
}
Table 
% \ref{tab:SystemKWHSQFT}
shows the relationship between heating and cooling degree days per square foot on electricity use for each of the tenure and structure type combinations.  These results are particularly troublesome because heating and cooling degree days, in conjunction with square footage, are one of the most reliable explanatory variables for electricity use.  Space heating and cooling are two major end-uses in most households.  The parameter estimates show that these reliable explanatory variables are only significant in a few rare cases.  There is a strong relationship heating and cooling degree days for owned single family detached structures, but only rented mobile homes show statistically significant reations to heating loads and only large appartments, owned or rented, for cooling loads.

@@

% Fri Apr  3 22:04:16 2015
{\small

@@

\caption{Orthodox kWh Model} \\ 

@@

@@

% Fri Apr  3 22:04:16 2015
{\small
\caption{Orthodox Square Foot Model} \\ 
(Intercept) & 1944.2850 & 75.4800 & 25.76 & 0.0000 \\ 
  RENTHELPTRUE & 182.1575 & 82.5453 & 2.21 & 0.0274 \\ 
  StrTenureOwnLgApartment & -1374.2383 & 67.6666 & -20.31 & 0.0000 \\ 
  StrTenureOwnMobile & -1095.7710 & 47.1356 & -23.25 & 0.0000 \\ 
  StrTenureOwnSFAttached & -493.4629 & 52.5900 & -9.38 & 0.0000 \\ 
  StrTenureOwnSmApartment & -776.3654 & 87.1475 & -8.91 & 0.0000 \\ 
  StrTenureRentLgApartment & -1393.2440 & 30.1078 & -46.28 & 0.0000 \\ 
  StrTenureRentMobile & -1202.7143 & 95.8133 & -12.55 & 0.0000 \\ 
  StrTenureRentSFAttached & -807.0103 & 62.9410 & -12.82 & 0.0000 \\ 
  StrTenureRentSFDetached & -561.3334 & 38.9760 & -14.40 & 0.0000 \\ 
  StrTenureRentSmApartment & -1142.2015 & 41.4263 & -27.57 & 0.0000 \\ 
  Income & 0.0079 & 0.0003 & 30.04 & 0.0000 \\ 
  reporttot & 11.6455 & 2.0454 & 5.69 & 0.0000 \\ 
  EDUCATIONNoHS & 45.4843 & 77.6015 & 0.59 & 0.5578 \\ 
  EDUCATIONHS & 77.1327 & 73.4168 & 1.05 & 0.2935 \\ 
  EDUCATIONSomeCol & 131.9180 & 74.1386 & 1.78 & 0.0752 \\ 
  EDUCATIONAA & 123.6675 & 77.9407 & 1.59 & 0.1126 \\ 
  EDUCATIONBA & 330.4375 & 75.4797 & 4.38 & 0.0000 \\ 
  EDUCATIONMA & 334.8239 & 80.7072 & 4.15 & 0.0000 \\ 
